\documentclass[../main/thesis_msc.tex]{subfiles}

\begin{document}
    \chapter*{Acknowledgments}
    \addcontentsline{toc}{chapter}{Acknowledgments}
    \phantomsection
    \thispagestyle{plain}

I would like to start by acknowledging Dr. Rainer Beck. It was an honour and a privilege to work under you. You were very kind and patient with me throughout this project. Your immense knowledge and love for the subject gave me courage to keep going with the project, in spite of several negative results. I would also like to thank Dr. Andreas Horneffer, for helping me with definately the most difficult part of my thesis. You were extremely supportive, explaining even the most fundamental and basic concepts involved in LOFAR data calibration. I also heartily thank Prof. Dr. Cristiano Porciani. You were one of the best teachers in my life. Your lectures were simply amazing, and your exams- a very humbling experience. Preparing for the Astro-Seminar under your guidance was also a lot of fun. I would also like to thank Prof. Dr. Michael Kramer, for supporting me during my thesis, and for letting me be a part of your amazing group. I owe my deep gratitude to Dr. Thushara Pillai and Dr. Jens Kauffmann for your willingness to help me, even when I was very new to the concept of `research'. Another person I am thankful for is Dr. Cathy Horellou. You were very helpful during my Sweden trip, and your crepes are really good! I would also like to thank Dr. Shane O' Sullivan for providing me with your codes, it would have taken me forever to write them myself. I would also like to thank Dr. Aritra Basu. Your understanding of the subject and your simple explanations for everything were extremely helpful. You were an amazing mentor and friend, and it was a shame you had to leave before the completion of my Masters. I am sure that my thesis would have been much better had you been around to clarify my doubts.\\
 \indent     I would also like to thank Kira Kuhn for being very helpful. It is indeed true what they say, `when in doubt, ask Kira!'. I would like to thank all my friends who were always there to keep my spirits high. I would like to especially thank Maja Kierdorf. After Andreas left the insitute, you were more of a teacher to me than anyone, taking time off your schedule to read my thesis and even coming in to explain the comments! I would also like to thank Yik Ki Ma, for proof reading my thesis (with such detailed suggestions!). I would also like to thank Nataliya Porayko for coming in and explaing how magnetic fields are studied.  \\
  \indent    I would like to thank my fortunes for giving me such amazing parents, whom I miss every single day! Mumma, your constant support and faith in me kept me going during this humbling journey that was my Masters. Papa, without your guidance and understanding, I would never have reached this juncture. I would also like to thank Shirley Joseph, my long distance friend. Life is always better when your best friend is there to gossip with, in spite of the long miles.  Last but not the least, I would like to thank Vishnu Balakrishnan, for always having my back, and keeping me happy with a constant supply of food. Next time people say I look `healthy', I shall let them know that you are the culprit. I hope that in years to come, some of your workaholic lifestyle would rub off on me, and help me become a better researcher.

    \newpage
    \mbox{}
    \thispagestyle{empty}
\end{document}
